Community biomass and species richness temporal trends reveal contrasting

### 2022-02-22 paper/method_figure.Rmd
Update figures

save_plot(
  get_mypath("figures/decreasing_biomass_network.png"),
  g,
  nrow = 3,
  ncol = 4,
  base_height = 4,
  base_width = 4)

@@

save_plot(
  get_mypath("figures/decreasing_biomass.png"), tps_bm_dec,
  nrow = 1,
  ncol = 1,
  base_height = 4,
  base_width = 7)

@@

save_plot(
  get_mypath("figures/increasing_biomass.png"), tps_bm_inc,
  nrow = 1,
  ncol = 1,
  base_height = 4,
  base_width = 7)
```

@@

plot_temporal_variable_lm <- function(
  .df = full_data2,
  var = "ct_ff",
  st = 15818) {
  tex <- .df %>%
    filter(station %in% st) %>%
    mutate(
      year = ymd(year, truncated = 2L)
    )

@@

    tex %>%
      ggplot(aes_string(x = "year", y = var)) +
      geom_point() +
      geom_smooth(aes(group = station), method = "lm", formula = y ~ x,
        size = 1, se = FALSE, color = "black") +
      labs(x = "Year", y = str_replace_all(var, var_replacement()))

@@

```{r}
tes <- map(dec_representative$station, ~plot_dyn_web(
    com = community_metrics,
    sem_df = NULL,
    station = .x,
#    .log = TRUE,
    stacked = TRUE, 
    color_species = NULL 
    ))
plot_grid(plotlist = tes)
```
```{r}
st_decreasing <- dec_representative$station[3]

p_dec_log_bm <- tes[[3]] +
  labs(color = "Species", fill = "Species") +
  theme(legend.position = "bottom")

save_plot(
  get_mypath("figures/p_dec_log_bm.png"),
  p_dec_log_bm,
  nrow = 1,
  ncol = 1,
  base_asp = 1.618,
  base_width = 7)
```
```{r}
tps_dec_inc <- map(c("ct_ff", "w_trph_lvl_avg", "log_rich_std", "piel_bm"),
  ~plot_temporal_variable_lm(st = st_decreasing, var = .x)
)
save_plot(
  filename = get_mypath("figures/net_str_dec_bm.png"),
  plot_grid(plotlist = tps_dec_inc),
  nrow = 2, ncol = 2,
  base_asp = 1.618,
  base_width = 5
)
```
```{r temporal foodwebs}

p <- get_network_temporal_plot(
  net_list = network_analysis,
  station = st_decreasing,
  selected_years = c(1996, 2006, 2016),
  node_color = my_species_color, scale_node_size = 0.027,
  par_options = par(mar = c(0,0,0,0)),
  log_abun = TRUE
)
g <- plot_grid(plotlist = map(p, ggdraw), ncol = 3)

save_plot(
  get_mypath("figures/decreasing_biomass_network.pdf"),
  g,
  ncol = 3,
  base_asp = 1.618,
  base_width = 7)
```

@@

>>>>

save_plot(
  get_mypath("figures/decreasing_biomass_network.pdf"),
  g,
  nrow = 3,
  ncol = 4,
  base_height = 4,
  base_width = 4)

@@

save_plot(
  get_mypath("figures/decreasing_biomass.pdf"), tps_bm_dec,
  nrow = 1,
  ncol = 1,
  base_height = 4,
  base_width = 7)

@@

save_plot(
  get_mypath("figures/increasing_biomass.pdf"), tps_bm_inc,
  nrow = 1,
  ncol = 1,
  base_height = 4,
  base_width = 7)
```

@@

plot_temporal_variable_lm <- function(
  .df = full_data2,
  var = "ct_ff",
  st = 15818,
  col_trend = "black",
  add_median = TRUE,
  col_median = "blue",
  size_line = 1
  ) {
  tex <- .df %>%
    filter(station %in% st) %>%
    mutate(
      year = ymd(year, truncated = 2L)
    )

@@

    p <- tex %>%
      ggplot(aes_string(x = "year", y = var)) +
      geom_point() +
      geom_smooth(
        aes(group = station), method = "lm", formula = y ~ x,
        size = size_line, se = FALSE, color = col_trend) +
      labs(x = "Year", y = str_replace_all(var, var_replacement()))

    if (add_median) {

      p <- p + 
        geom_hline(yintercept = median(tex[[var]]), col = col_median, size =
          size_line)
    }
    return(p)
}

@@

```{r}
color_tes <- map(dec_representative$station,
  ~set_color_species(
  node_list = community_metrics %>%
  filter(station == .x) %$%
  .$sp_vector %>%
  reduce(., c) %>%
  names(.) %>%
  unique(),
  resource_list = metaweb_analysis$resource,
  col_resource = NULL
  )
)
names(color_tes) <- as.character(dec_representative$station)

tes <- map(dec_representative$station, ~plot_dyn_web(
    com = community_metrics,
    sem_df = NULL,
    station = .x,
#    .log = TRUE,
    stacked = TRUE,
    color_species = color_tes[[as.character(.x)]]
    ))

names(tes) <- as.character(dec_representative$station)
plot_grid(plotlist = tes)
```
```{r}

st_decreasing <- dec_representative$station[3]

p_dec_log_bm <- tes[[as.character(st_decreasing)]] +
  labs(color = "Species", fill = "Species") +
  theme(legend.position = c(.2, .8), legend.direction = "horizontal")

save_plot(
  get_mypath("figures/p_dec_log_bm.pdf"),
  p_dec_log_bm,
  nrow = 1,
  ncol = 1,
  base_height = 6.6,
  base_asp = 1.2
  )
```
```{r}
v_colors =  viridis(n = 2, begin = 0.5, end = 1)
names(v_colors) <- c("tps", "sp")

tps_dec_inc <- map(c("log_bm_std", "log_rich_std", "ct_ff", "w_trph_lvl_avg", "piel_bm"), # 
  ~plot_temporal_variable_lm(st = st_decreasing, var = .x, col_median =
    v_colors["sp"], col_trend = v_colors["tps"]) +
    theme(axis.title = element_text(size = 12))
)
# Increase point size
tps_dec_inc  <- map(tps_dec_inc, function(x) {
  x$layers[[1]]$aes_params$size <- 4
  return(x)
})

# Delete x axis
#tps_dec_inc[-length(tps_dec_inc)]  <- map(tps_dec_inc[-length(tps_dec_inc)], function(x) {
#  x + theme(
#    axis.text.x = element_blank(),
#    axis.ticks.x = element_blank(),
#    axis.title.x = element_blank()
#  )
#})

save_plot(
  filename = get_mypath("figures/net_str_dec_bm.pdf"),
  plot_grid(plotlist = tps_dec_inc, nrow = 1, align = "h", axis = "l"),
  ncol = length(tps_dec_inc), nrow = 1, 
  base_height = 2.6,
  base_asp = 1.2 
)
theme_get()$text
```

```{r temporal foodwebs}
p <- get_network_temporal_plot(
  net_list = network_analysis,
  station = st_decreasing,
  selected_years = c(1995, 2005, 2015),
  node_color = color_tes[[as.character(st_decreasing)]],
  scale_node_size = 0.027,
  par_options = par(mar = c(0,0,0,0)),
  log_abun = TRUE
)
g <- plot_grid(plotlist = map(p, ggdraw), ncol = 3)

save_plot(
  get_mypath("figures/decreasing_biomass_network.pdf"),
  g,
  ncol = 3, nrow = 1,
  base_width = 7, base_height = 7)

```

@@

```{r}
loadd(station_analysis, st_mono_trends_stable_rich_bm)
```
```{r}
fr_map <- ne_countries(scale = "medium", returnclass = "sf") %>%
  filter(geounit == "France") %>%
  st_transform(crs = 2154)
st <- station_analysis %>%
  filter(id %in% st_mono_trends_stable_rich_bm) %>%
  st_transform(crs = 2154)

p <- ggplot() +
    geom_sf(data = st_geometry(fr_map), lwd = 0) +
    geom_sf(data = st_geometry(st)) +
    coord_sf(
      xlim = st_bbox(st)[c(1, 3)],
      ylim = st_bbox(st)[c(2, 4)]
    ) +
  theme_bw() +
  theme(
    panel.border = element_blank(), panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    axis.ticks = element_blank(), axis.text = element_blank())
p
```
```{r}
save_plot(
  p,
  base_height = 12,
  base_asp = 1.618,
  file = get_mypath("figures", "simple_map_matmet.pdf")
)
```
